ms_results

### 2023-02-07 ms_results.Rmd

Another measure of the degree of globalization is the share of production exported. Domestic exports increased to `r round(percent_export_total_dom_2019, 1)`% of production in 2019, up from `r round(percent_export_total_dom_2019, 1)`% in 1996. while total exports reached 33% of all production in 2019. For comparison, the share of cereal production exported grew from around 10% in the late 1990s to 17% in the 2020s (Clapp 2022). Increasing marine capture export volumes despite stagnating production resulted in marine capture products having the greatest share of production destined for export (`r round(percent_marine_capture_exported_2019, 1)`% of production) and experienced the largest increases in the share exported, and largest increases in the share exported (Fig 2b). Aquaculture production more than doubled from 1996 to 2019, but aquaculture exports grew even faster, leading to an increasing share exported (Fig 2b). Despite increases, inland aquaculture still had the lowest share of production destined for export in 2019 (domestic exports represented only `r round(percent_inland_aqua_exported_2019, 1)`% of production) (Fig 1b). This finding clarifies prior debates about the orientation of aquaculture, while export trends suggest a need to consider international markets when crafting nutrition-sensitive policies (Golden et al. 2017; Belton et al 2018; Gephart et al. 2019).

>>>>

Another measure of the degree of globalization is the share of production exported. Domestic exports increased to `r round(percent_export_total_dom_2019, 1)`% of production in 2019, up from `r round(percent_export_total_dom_1996, 1)`% in 1996. while total exports reached 33% of all production in 2019. For comparison, the share of cereal production exported grew from around 10% in the late 1990s to 17% in the 2020s (Clapp 2022). Increasing marine capture export volumes despite stagnating production resulted in marine capture products having the greatest share of production destined for export (`r round(percent_marine_capture_exported_2019, 1)`% of production) and experienced the largest increases in the share exported, and largest increases in the share exported (Fig 2b). Aquaculture production more than doubled from 1996 to 2019, but aquaculture exports grew even faster, leading to an increasing share exported (Fig 2b). Despite increases, inland aquaculture still had the lowest share of production destined for export in 2019 (domestic exports represented only `r round(percent_inland_aqua_exported_2019, 1)`% of production) (Fig 1b). This finding clarifies prior debates about the orientation of aquaculture, while export trends suggest a need to consider international markets when crafting nutrition-sensitive policies (Golden et al. 2017; Belton et al 2018; Gephart et al. 2019).
